Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks

### 2023-04-24 paper.tex
fixed greater-equal

In base of some of this concept, 
 we have several different MARL, like cooperative MARL (i.e., the reward function incetivize collective outcomes)
 heterogenous MARL (i.e., the agents have different action space and policy) and
 homogenous MARL (i.e., the agents have the same action space and policy).
%  
In particular, in this work we consider homogenous many agent RL, 
 where, N >> 2 and action space of each agent and the policy is the same (i.e., the agents are interchangeable)
\section{Field-informed Reinforcement Learning}
\label{sec:approach}
\ga{Page budget: 2/3 pages \\}
\ga{Plan: we should discuss the approach in detail, including the system model, the learning dynamics.
Particularly, I would like to highlight how the each node in the graph is a local controller,
but it could be see as a global evolution, therefore we can use global information to inform the local controller.}
\subsection{System model}
\ga{Plan: 
  discussion about typical AC evalaution model, specifying how GNN (with 1-hop information diffusion)
  can be easily integrate with this distributed model
}
\subsection{Learning dynamics}
\ga{
  Plan: discuss about the choosing approach, that is Centralised Training and Distributed Execution.
  Particularly, we use DQN in which the neural network is a GNN. So, the dataset consist in a set of graphs,
  where each graph is a snapshot of the system. 
  The target is the Q-value of the action taken in the current state.
  Explain how this can be then use for distributed controller.
}
\section{Evaluation}
\label{sec:eval}
\ga{Page budget: 2 pages \\}
\ga{Plan: we should discuss the robot aggregation scenario, specifiying the state space, the action space, the reward function.
I dunno if it makes sense to discuss the variants (i.e., fixed area, two ares and moving area). We will see.
}
\subsection{Scenario}

>>>>

In base of some of this concept, 
 we have several different MARL, like cooperative MARL (i.e., the reward function incetivize collective outcomes)
 heterogenous MARL (i.e., the agents have different action space and policy) and
 homogenous MARL (i.e., the agents have the same action space and policy).
%  
In particular, in this work we consider homogenous many agent RL, 
 where, $N \geq 2$ and action space of each agent and the policy is the same (i.e., the agents are interchangeable)
\section{Field-informed Reinforcement Learning}
\label{sec:approach}
\ga{Page budget: 2/3 pages \\}
\ga{Plan: we should discuss the approach in detail, including the system model, the learning dynamics.
Particularly, I would like to highlight how the each node in the graph is a local controller,
but it could be see as a global evolution, therefore we can use global information to inform the local controller.}
\subsection{System model}
\ga{Plan: 
  discussion about typical AC evalaution model, specifying how GNN (with 1-hop information diffusion)
  can be easily integrate with this distributed model
}
\subsection{Learning dynamics}
\ga{
  Plan: discuss about the choosing approach, that is Centralised Training and Distributed Execution.
  Particularly, we use DQN in which the neural network is a GNN. So, the dataset consist in a set of graphs,
  where each graph is a snapshot of the system. 
  The target is the Q-value of the action taken in the current state.
  Explain how this can be then use for distributed controller.
}
\section{Evaluation}
\label{sec:eval}
\ga{Page budget: 2 pages \\}
\ga{Plan: we should discuss the robot aggregation scenario, specifiying the state space, the action space, the reward function.
I dunno if it makes sense to discuss the variants (i.e., fixed area, two ares and moving area). We will see.
}
\subsection{Scenario}
